\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Barney Desmond}
{+61-413-476-139 (mobile)\\
barneydesmond@gmail.com\\
Sydney, Australia}

% SRE role: https://jobs.lever.co/palantir/da5b54d1-8673-479b-9091-36f71d752ccb

% Outline
% * Ops and uptime
% * Designing new systems for deployments
% * Administering and troubleshooting
% * Maintaining DBs
%
% Bottom line: Keep things running, make them better and more reliable.

% Requirements
% * Linux
% * Scripting in Bash/Python/Ruby/Perl
% * Monitoring and Nagios
% * TCP/IP networking
% * Managing DBs or search engines, Postgres, MySQL, Oracle, Cassandra or ElasticSearch
% * Work independent
% * On-call rotation
% * OpSec and best practices

% Preferred
% * BSc/MS in Comp Sci
% * Virtualization using VMWare ESX, KVM, Xen, or Docker
% * Puppet or Chef
% * Server hardware and/or AWS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Ten-Second Summary}
\multicolumn{2}{p{16cm}}{
\setstretch{1.2}
I have over a decade of experience designing and running Linux systems. I'm
used to solving difficult problems, and I take a rigorous approach to ensure
the job is done properly. My background is in managing the full stack for
web-facing applications, but my interests are much broader and I quickly pick
up new skills as needed.
}
\hugeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment experience}

\textbf{Enterprise Linux administrator} -- NSW Dept. of Education & \hspace{3mm}Aug 2015 -- Present \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
% * Ops and uptime
% * Designing new systems for deployments
% * Administering and troubleshooting
% * Maintaining DBs
%
% Bottom line: Keep things running, make them better and more reliable.
\item Built, monitored, and maintained a large fleet of RHEL systems with a commitment to availability and security. Demonstrated performance with open access to Icinga dashboards and server metrics. Systems were secured through appropriate application of industry best practices.
% VRA API scripting with Python and Makefiles
\item Wrote tools in Bash and Python to help build new systems rapidly with VMware's APIs, followed with Puppet for ongoing management.
% Git branches for Puppet envs, we never did manage to shift to the r10k/Puppetfile method though
\item Introduced Git branches and pull requests in Bitbucket for our Puppet repo, allowing proper oversight of changes. This also enabled multiple sysadmins to work on Puppet code without affecting each other.
% Preflight checks across various RHEL versions, picky partitioning with SAP systems, use of tingle for hands-off patching
\item Systematically eliminated points of failure that prevented timely patching of systems, with an emphasis on proactive monitoring to discover problems sooner.
% Onboarding+departure of staff, managing accounts in LDAP for services, shift to LDIF templating for this
\item Wrote extensive documentation for processes to ensure repeatability and ease of future automation. This also served as a useful training reference for new staff, as a lot of organisational knowledge is latent.
% MW team's SSO stuff, pushed to Satellite, deployed with Puppet
\item Automated packaging and deployment of internally developed software using Mock and RedHat Satellite.
% Proof-of-concept with PG 9.6, deployed PG10, full auto config of replication and backups, start deploying Barman
\item Led our internal deployment of PostgreSQL, and advised on design, performance, and migration concerns.

% DCR, migration to cloud, use of VRA for VM deployment, new network segment organisation w/ firewalls
% XXX: not sure I have enough room for this one
%\item Worked across teams to help drive changes to virtualisation, storage, and networking.
\end{itemize}
}
\tinyskip

\textbf{R\&D Engineer} -- Anchor & \hspace{3mm}Aug 2013 -- Aug 2015 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Worked as part of an internal team on tooling and efficiency measures to support frontline sysadmins.
\item Languages and tools were chosen for their suitability to the task. This broadly included Python, Ruby and Haskell for app code, and Postgres, Redis, Elasticsearch, and Ceph for the backend technologies.
\item Wrote \emph{UMAD}, a knowledge search engine spanning disparate sources of information, including our wiki, support ticketing system, domain registrations, and CRM.
\item Internal software was deployed using \emph{Docker} containers, onto our in-house \emph{Openstack} cluster.
\end{itemize}
}
\tinyskip

\textbf{Technical writer} -- Anchor & Nov 2011 -- Aug 2013 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Wrote and edited thousands of pages of internal procedures, guides, and documentation, supporting every facet of the business, targeted for different audiences as required.
\item Managed deadlines presented by multiple teams, ensuring documentation was consistently delivered on-time.
\item Published 200+ articles on the blog, written to a specifically tech-savvy audience, to entertain and enlighten.
\item Developed training modules for new staff to get them up to speed and productive as soon as possible.
\item Started and maintained a new public-facing knowledgebase for customers.
\end{itemize}
}
\tinyskip

\textbf{Senior Linux sysadmin} -- Anchor & Apr 2007 -- Nov 2011 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Build and administration of RHEL and Debian servers for customers, both physical and virtual (VMware, Xen, KVM).
\item Upgraded internal monitoring systems to implement escalation of alerts, and more in-depth monitoring.
\item Developed processes for rapid virtualisation of physical servers, helping reduce operating costs.
\item Mentored new staff, working closely to get them settled in and up to speed.
\end{itemize}
}

\end{resumeblock}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
%\newpage



\begin{skillz}{Knowledge and experience}

\resumeitem{Operating Systems}{Extensive Linux background, primarily Redhat (RHEL and Fedora) and Debian. Exposure to Windows 7/8/10, Server 2008 and 2012, some OS X}
\hugeplusskip

\resumeitem{Languages}{Heavy user of Python and shell scripting, fluent in C, PHP, Perl, some Javascript, Ruby, and Java}
\hugeplusskip

% * BSc/MS in Comp Sci
% * Virtualization using VMWare ESX, KVM, Xen, or Docker
% * Puppet or Chef
% * Server hardware and/or AWS

\resumeitem{Development}{Daily user of Git (standalone, Github, Bitbucket), svn, agile methodologies, deployment best practices with CI/CD, packaging in RPM and DEB formats, containerisation, debugging with tools such as gdb}
\hugeplusskip

\resumeitem{Networking}{In-depth knowledge covering architecture and design, capacity planning, addressing and subnetting, routing and associated protocols, high availability, debugging, performance, IPsec and OpenVPN, IPv6, firewalls}
\hugeplusskip

\resumeitem{Databases}{Well versed in PostgreSQL and its replication features, MySQL, Redis, and ElasticSearch. I have developed my own applications against them, and understand performance and integrity concerns from both sides.}
\hugeplusskip

\resumeitem{Hardware}{Plenty of hands-on datacentre experience, and I am thoroughly familiar with the realities of how systems are built in practice. The recent trend towards virtualisation of workloads has changed how we work, but the fundamentals remain the same.}
\hugeplusskip

\resumeitem{Virtualisation}{Have deployed and managed VMs with KVM, Xen, and VMware, with solid knowledge of all the layers. Familiar with AWS services and corresponding APIs, including Terraform for automations. Some experience with Docker containers at small scale.}
\hugeplusskip

\resumeitem{Security}{I have a pragmatic approach to security and recognise that it is a core operational concern. I have a particular interest in cryptography, risk assessment, and policy rooted in best practices.}
\hugeplusskip

\resumeitem{Automation}{Ansible, Puppet, automated OS installation with tools such as Kickstart and d-i, scripting with core unix utilities, etc.}
\hugeplusskip

\resumeitem{People}{I am first and foremost a good listener. I communicate clearly and effectively, and can explain complex concepts to others regardless of their level of familiarity.}
\hugeplusskip

\end{skillz}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
Bachelor of Science (Computer Science)\newline
University of New South Wales & 2002 -- 2006
\end{resumeblock}
\tinyskip


\end{document}
