\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Barney Desmond}
{+61-413-476-139 (mobile)\\
barneydesmond@gmail.com\\
Sydney, Australia}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Ten-Second Summary}
\multicolumn{2}{p{16cm}}{
A Linux sysadmin turned technical writer, I'm a hacker at heart who loves teaching people new things. I pull things apart, I learn about them, I understand them. Then I write about them.
}
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment experience}

\resumeitem{Nov 2011 -- Present}{Anchor (webhosting provider) -- Technical writer\\ &
\begin{itemize}[topsep=-2mm,itemsep=1mm,parsep=1mm]
\item Wrote and edited thousands of pages of documentation for the company's internal wiki, supporting every facet of the business (now over 40 employees).
\item Managed the deadlines presented to me by technical, sales and management teams, and ensured documentation was consistently delivered on-time.
\item Published over 200 articles on the company blog, most technical, written to a specifically tech-savvy audience, to entertain and enlighten.
\item Undertook initiatives to track and grow readership of the blog, using scientific methods and analysis to drive towards 10,000 hits/month.
\item Developed all new training modules for new staff to get them up to speed and productive as soon as possible.
\item Wrote and proofread various marketing materials as needed, including flyers, posters, website copy, case studies and press releases.
\item Initiated and maintained a new public-facing knowledgebase for customers.
\end{itemize}
}
\largeskip

\resumeitem{Apr 2007 -- Nov 2011}{Anchor -- Senior systems administrator\\ &
\begin{itemize}[topsep=-2mm,itemsep=1mm,parsep=1mm]
\item Mentored new staff, working closely to get them settled in and up to speed.
\item Developed automation tools to allow L1 support staff to safely and efficiently perform L2 tasks.
\item Performed forensic analysis and reporting following security breaches.
\item Developed processes for rapid virtualisation of physical servers, helping the company rapidly reduce ongoing costs.
\end{itemize}
}
\largeskip

\resumeitem{Aug 2005 -- Feb 2007}{Australian Customs Service -- Immigration officer\\ &
\begin{itemize}[topsep=-2mm,itemsep=1mm,parsep=1mm]
\item Processed passengers and provided legal compliance advice and assistance.
\item Held a PROTECTED security clearance
\end{itemize}
}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
\resumeitem{2002--2006}{Bachelor of Science (Computer Science)\\
	& University of New South Wales}
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newpage


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{How I work}

\resumeitem{Modus operandi}{Marketing and sales, hardcore technical analysis or end-user guides, I understand the target audience and write accordingly.}
\largeskip

\resumeitem{Medium}{Everything is hypertext these days (but I'll happily do print) so I write copy, create diagrams and screenshots, and do photos and A/V if it's most appropriate for the subject.}
\largeskip

\resumeitem{Software}{Browser and vim for wikis and markup, Inkscape/Gimp/Photoshop as needed for imagery, Audition and Premiere for audio and video. I learn whatever it takes to get the job done.}
\largeskip

\resumeitem{It's all about text}{Markdown is my go-to for almost anything that isn't in a wiki, and my favourite wiki is Moin, though I'm comfortable with with anything else (Confluence included, of course!). \LaTeX{} for beautiful documents. Will cut raw HTML and CSS in a pinch.}
\largeskip

\resumeitem{Technical background}{As a former webhosting sysadmin, my knowledge covers a very wide gamut including: Linux and Windows, programming (both scripting and compiled languages), databases, networking, security and automation.}
\largeskip

\resumeitem{Time management}{I'm a big fan of kanban-style management for its visibility and simple nature that lets me coordinate with my team and Get Things Done quickly.}
\largeskip

\resumeitem{People}{I can get along with just about anybody. Many years of customer-facing experience have made me a good listener, measured in response, professional and eloquent. I'm always ready to share my knowledge, and can present confidently as needed.}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{interestsblock}{Interests \& activities}


\begin{itemize}[topsep=-2mm,itemsep=1mm,parsep=1mm]

\item Japanese language and culture
\item Photography
\item Sewing and costuming

\end{itemize}
&

\begin{itemize}[topsep=-2mm,itemsep=1mm,parsep=1mm]

\item Cryptography
\item Imaging metadata
\item Software translation and localisation

\end{itemize}


\end{interestsblock}


\end{document}
