\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Barney Desmond}
{+61-413-476-139 (mobile)\\
barneydesmond@gmail.com\\
Sydney, Australia}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Ten-Second Summary}
\multicolumn{2}{p{16cm}}{
\setstretch{1.2}
I have clocked up over eight years of commercial webhosting and sysadmin
experience at Anchor, a leading Australian hosting company. I've designed,
deployed, and managed large complex systems. Automation, proper processes, and
documentation ensures they're reliable and maintainable.
}
\hugeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment experience}

\textbf{R\&D Engineer} -- Anchor & \hspace{3mm}Aug 2013 -- Present \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Worked as part of a small internal team on tooling and efficiency measures to support sysadmins.
\item Wrote \emph{UMAD}, a knowledge search engine spanning disparate sources of information, including our wiki, support ticketing system, domain registrations, and CRM.
\item \emph{Machiavelli}, a graphing interface for Nagios metrics
\item \emph{Vaultaire} and associated microservices, a time-series database for large-scale storage of monitoring metrics, built on top of the Ceph datastore.
\item Integration of \emph{Shibboleth} with existing systems to provide auth for local and third-party services. \emph{OAuth2} for authorisation in our apps.
\item Used \emph{CoreOS} images and \emph{Docker} containers to deploy our apps onto our in-house \emph{Openstack} cluster.
\item \emph{Jenkins} and \emph{Travis} CI for packaging and deployment to private repos, in addition to comprehensive testing.
\item Lots of distro packaging for RPMs and DEBs.
\end{itemize}
}
\tinyskip

\textbf{Technical writer} -- Anchor & Nov 2011 -- Aug 2013 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Wrote and edited thousands of pages of internal documentation, supporting every facet of the business.
\item Managed deadlines presented by multiple teams, ensuring documentation was consistently delivered on-time.
\item Published over 200 articles on the blog, written to a specifically tech-savvy audience, to entertain and enlighten.
\item Developed all new training modules for new staff to get them up to speed and productive as soon as possible.
\item Initiated and maintained a new public-facing knowledgebase for customers.
\end{itemize}
}
\tinyskip

\textbf{Senior systems administrator} -- Anchor & Apr 2007 -- Nov 2011 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Upgraded internal monitoring systems to implement escalation of alerts
\item Mentored new staff, working closely to get them settled in and up to speed.
\item Developed automation tools to allow L1 support staff to safely and efficiently perform L2 tasks.
\item Performed forensic analysis and reporting following security breaches.
\item Developed processes for rapid virtualisation of physical servers, helping reduce operating costs.
\end{itemize}
}
\tinyskip

\textbf{Immigration officer} -- Australian Customs Service & Aug 2005 -- Feb 2007 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Processed passengers and provided legal compliance advice and assistance.
\item Held a PROTECTED security clearance
\end{itemize}
}

\end{resumeblock}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
%\newpage



\begin{skillz}{Knowledge and experience}

\resumeitem{Operating Systems}{Strong knowledge of Linux (primarily Debian and
Redhat) and Windows}
\shortskip

\resumeitem{Languages}{Lots of Python, shell, Perl, PHP, C, some Ruby and Java}
\shortskip

\resumeitem{Databases}{PostgreSQL, MySQL, some MSSQL}
\shortskip

\resumeitem{Networking}{Architecture, addressing, routing, debugging, performance, VPN, IPv6, firewalls}
\shortskip

\resumeitem{Security}{Policy, risk assessment, reporting, auditing, analysis, best practice, crypto}
\shortskip

\resumeitem{Automation}{Puppet, automated OS installation, scripting with core unix utilities, etc.}
\shortskip

\resumeitem{Webapps}{LAMP stack, nginx, WSGI, Rails, Tomcat}
\shortskip

\resumeitem{People}{Listener, amicable, professional, courteous, level-headed}
\largeskip

\resumeitem{Technical background}{As a sysadmin, my knowledge covers a broad gamut, including Linux and Windows, programming, databases, networking, security and automation.}
\largeskip

\resumeitem{Work methodologies}{Kanban and agile, using both whiteboards and Trello. Some exposure to Jira as well, but we don't like it as much. Daily standups are a thing.}
\largeskip

\resumeitem{People}{I can get along with just about anybody. Many years of customer-facing experience have made me a good listener, measured in response, professional and eloquent. I'm always ready to share my knowledge, and can present confidently.}
\largeskip

\end{skillz}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
Bachelor of Science (Computer Science)\newline
University of New South Wales & 2002 -- 2006
\end{resumeblock}
\tinyskip


\end{document}
