\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Barney Desmond}
{+61-413-476-139 (mobile)\\
barneydesmond@gmail.com\\
Sydney, Australia}

% Security Engineering Team Lead
% * Lead
% * Drive change
% * influence, guide, mentor and lead on all aspects of product security
% * Guide the team and grow them, set a standard
% * Design reviews, code reviews, threat modelling, work with engineering groups
% * Ability to code, Python/Go/Java

% Experience
% * Leading small teams
% * Understand app security
% * Coding experience

% Desired
% * Published research
% * Open source work
% * SEng or DevOps background


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Ten-Second Summary}
\multicolumn{2}{p{16cm}}{
\setstretch{1.2}
I have 12+ years of professional experience as a Linux sysadmin, solving
difficult problems and making things work in fast-paced environments. More
recently I've shifted to supporting \emph{products} rather than infrastructure,
taking ownership and applying my experience to ensure the reliability and
security of systems.
}
\hugeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment experience}

\textbf{Enterprise Linux administrator} -- NSW Dept. of Education & \hspace{3mm}Aug 2015 -- Present \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
% RHEL7 hardening guide based on various industry standards and best practice advice
\item Developed and improved security policy for access to Linux systems based on best practices.
\item Designed OS hardening process for new RHEL7 deployments, implemented using Ansible and Puppet.
% LDAP server password hashing config, sshd configs on servers
\item Performed security config auditing and remediation across our fleet of servers.
% Remote access with staff account fro overseas, flagging odd activity in Splunk
\item Post-incident analysis to inform our response to security incidents.
% Literally EVERYTHING I was doing, provisioning, config changes, etc.
\item Automated many common processes to reduce human error and improve service turnaround.
% My protopages section in the wiki, how stuff works, what connects to what, how monitoring autoprov works
\item Wrote processes and documentation so I could educate new coworkers on internal assumed knowledge.
% Huge DCR project, analysing existing services so they could be lifted while maintaing same functionality
\item Planned migration or replacement of legacy systems, switching cfengine to Puppet for management.
\end{itemize}
}
\tinyskip

\textbf{R\&D Engineer} -- Anchor & \hspace{3mm}Aug 2013 -- Aug 2015 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Worked as part of an internal team on tooling and efficiency measures to support frontline sysadmins.
\item Languages and tools were chosen for their suitability to the task. This broadly included Python, Ruby and Haskell for app code, and Postgres, Redis, Elasticsearch, and Ceph for the backend technologies.
\item Wrote \emph{UMAD}, a knowledge search engine spanning disparate sources of information, including our wiki, support ticketing system, domain registrations, and CRM.
\item \emph{Vaultaire} and associated microservices, a time-series database for large-scale storage of monitoring metrics, built on top of the Ceph datastore.
\item Internal software was deployed using \emph{Docker} containers, onto our in-house \emph{Openstack} cluster.
\item \emph{Jenkins} and \emph{Travis} CI for packaging and deployment to private repos, in addition to comprehensive testing.
\end{itemize}
}
\tinyskip

\textbf{Technical writer} -- Anchor & Nov 2011 -- Aug 2013 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Wrote and edited thousands of pages of internal procedures, guides, and documentation, supporting every facet of the business, targeted for different audiences as required.
\item Managed deadlines presented by multiple teams, ensuring documentation was consistently delivered on-time.
\item Published 200+ articles on the blog, written to a specifically tech-savvy audience, to entertain and enlighten.
\item Developed all new training modules for new staff to get them up to speed and productive as soon as possible.
\item Initiated and maintained a new public-facing knowledgebase for customers.
\end{itemize}
}
\tinyskip

\textbf{Senior Linux sysadmin} -- Anchor & Apr 2007 -- Nov 2011 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Upgraded internal monitoring systems to implement escalation of alerts.
\item Introduced Puppet for automation of customer server builds, replacing cfengine.
\item Mentored new staff, working closely to get them settled in and up to speed.
\item Forensic analysis and reporting following security breaches.
\item Developed processes for rapid virtualisation of physical servers, helping reduce operating costs.
\end{itemize}
}

\end{resumeblock}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
%\newpage



\begin{skillz}{Knowledge and experience}

\resumeitem{Operating Systems}{Extensive Linux background, primarily Redhat (RHEL and Fedora) and Debian. Exposure to Windows 7/8/10, Server 2008 and 2012, some OS X}
\hugeplusskip

\resumeitem{Languages}{Heavy use of Python, shell, Perl, PHP, C, some Ruby and Java, Haskell}
\hugeplusskip

\resumeitem{Development}{Git (standalone, Github, Bitbucket), svn, development methodologies, testing regimes, deployment best practices with CI/CD, packaging in RPM and DEB formats, containerisation, debugging tools}
\hugeplusskip

\resumeitem{Networking}{Architecture and design, capacity planning, addressing and subnetting, routing and associated protocols, high availability, debugging, performance, IPsec and OpenVPN, IPv6, firewalls}
\hugeplusskip

\resumeitem{Hardware}{I have plenty of hands-on datacentre experience and am thoroughly familiar with the realities of how systems are built in practice}
\hugeplusskip

\resumeitem{Databases}{PostgreSQL (with replication), MySQL, SQLite, Redis}
\hugeplusskip

\resumeitem{Security}{Policy, risk assessment, reporting, auditing, analysis, best practice, cryptography}
\hugeplusskip

\resumeitem{Automation}{Ansible, Puppet, automated OS installation with tools such as Kickstart and d-i, scripting with core unix utilities, etc.}
\hugeplusskip

\resumeitem{Webapps}{Common LAMP stack, nginx, WSGI, Rails via Thin/Unicorn/Passenger, Tomcat}
\hugeplusskip

\resumeitem{Scalability \& clustering}{HAproxy, Corosync and Pacemaker, DRBD}
\hugeplusskip

\resumeitem{People}{I am first and foremost a good listener. I communicate clearly and effectively in any medium, and can explain complex concepts to others regardless of their level of familiarity.}
\hugeplusskip

\end{skillz}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
Bachelor of Science (Computer Science)\newline
University of New South Wales & 2002 -- 2006
\end{resumeblock}
\tinyskip


\end{document}
