% Andrew McNabb's Resume
% Created: 7 Jan 2004
% Last Modified: 17 Jul 2004

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Andrew McNabb}
\newcommand{\addr}{123 Main St., Springfield, AA 12345}
\newcommand{\phone}{(123) 456-7890}
\newcommand{\email}{aaaaaaa@aaaaa.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsec}{Brigham Young University}{Provo, UT}{Majoring in Computer Science and in Mathematics}
		\ressubitem{GPA: 3.77 (overall), 3.77 (CS major), 3.90 (Math major)}
		\ressubitem{Projected Graduation Date: May, 2006}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

	\begin{ressubsec}{BYU Computer Science Department}{Provo, UT}{System Programmer: June 2003--present}
		\ressubitem{Manage 200 Linux and 150 Windows 2000 lab workstations.}
		\ressubitem{Maintain department Linux servers and document their configuration.}
		\ressubitem{Develop tools and scripts to improve reliability and functionality of the network.}
		\ressubitem{Assist users with problems and write tutorials and documentation.}
	\end{ressubsec}

	\begin{ressubsec}{Argus Systems Group, Inc.}{Champaign, IL}{System Administrator: March, 1997--August, 2000}
		\ressubitem{Configured servers, maintained inventory, and managed tape backup system.}
		\ressubitem{Prepared all product distribution media (including bootable CDs).}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

	\resitem{\textbf{Operating Systems:} Linux (Gentoo, Red Hat, and Debian), Mac OS 9 and X, UNIX (several variants), Windows 98/2000/XP}

	\begin{reslist}{Computer Languages:}

		\ressubitem{Proficient in C, C++, HTML, Java, \LaTeX, PHP, UNIX Shells}

		\ressubitem{Familiar with Perl, SQL}

	\end{reslist}

	\begin{reslist}{Tools and Systems:}

		\ressubitem{Proficient in Apache, BIND, CVS/RCS, Make, GnuPG, SSHD, VI}

		\ressubitem{Familiar with Kerberos, MySQL, NFS, OpenLDAP, OpenSSL, Postfix, Samba}

	\end{reslist}


\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

	\resitem{Served a voluntary two-year mission in Serbia and Bulgaria (2001--2003).  Speak fluent Serbian and basic Bulgarian.}

	\resitem{As a member and president of the BYU Unix Users Group, assist new Linux users and participate in presentations and discussions on advanced topics (2003--present).}

	\resitem{Manage a heterogeneous home network and family server (1996--present).}

	\resitem{Received a National Merit Scholarship.}

	\resitem{Co-authored ``Interacting Quantitative Trait Loci Control Phenotypic Variation in Murine Estradiol-Regulated Responses,'' \textit{Endocrinology} 140 no. 2 (1999).}

	\resitem{Awarded Eagle Scout Rank, Boy Scouts of America (1996).}


\end{ressection}


\end{document}
