\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}

\include{cv-commands}

\begin{document}

\setmainfont

\header
{Barney Desmond}
{+61-413-476-139 (mobile)\\
barneydesmond@gmail.com\\
Sydney, Australia}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Ten-Second Summary}
\multicolumn{2}{p{16cm}}{
\setstretch{1.2}
I have over a decade of professional experience as a Linux sysadmin, in both
commercial and government settings. I've designed, deployed, and managed large
complex systems. Automation, proper processes, and documentation ensures
they're reliable and maintainable.
}
\hugeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment experience}

\textbf{Enterprise Linux administrator} -- NSW Dept. of Education & \hspace{3mm}Aug 2015 -- Present \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Deployed automated patching for 1000+ RHEL hosts, reducing hands-on effort by an order of magnitude.
\item Developed data gathering and analysis tools to aid internal reporting processes.
\item Automated RPM packaging for internally maintained software, deployed to servers via RedHat Satellite.
\item Performed risk assessment and provided recommendations as part of change management procedures.
\item Partnered with other business units to design, develop, and deploy new systems.
\item Scripted and automated many common procedures to improve efficiency and reduce errors.
\item Updated large amounts of documentation and processes to bring them to an auditable standard.
\item Wrote onboarding docs for new staff members, reducing the time needed for face-to-face training.
\end{itemize}
}
\tinyskip

\textbf{R\&D Engineer} -- Anchor & \hspace{3mm}Aug 2013 -- Aug 2015 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Worked as part of a small internal team on tooling and efficiency measures to support sysadmins.
\item Languages and tools were chosen for their suitability to the task. This broadly included Python, Ruby and Haskell for app code, and Postgres, Redis, Elasticsearch, Ceph, and Druid for the backend technologies.
\item Wrote \emph{UMAD}, a knowledge search engine spanning disparate sources of information, including our wiki, support ticketing system, domain registrations, and CRM.
\item \emph{Machiavelli}, a graphing interface for Nagios metrics.
\item \emph{Vaultaire} and associated microservices, a time-series database for large-scale storage of monitoring metrics, built on top of the Ceph datastore.
\item Used \emph{CoreOS} images and \emph{Docker} containers to deploy our apps onto our in-house \emph{Openstack} cluster.
\item \emph{Jenkins} and \emph{Travis} CI for packaging and deployment to private repos, in addition to comprehensive testing.
\end{itemize}
}
\tinyskip

\textbf{Technical writer} -- Anchor & Nov 2011 -- Aug 2013 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Wrote and edited thousands of pages of internal procedures, guides, and documentation, supporting every facet of the business, targeted for different audiences as required.
\item Managed deadlines presented by multiple teams, ensuring documentation was consistently delivered on-time.
\item Published 200+ articles on the blog, written to a specifically tech-savvy audience, to entertain and enlighten.
\item Developed all new training modules for new staff to get them up to speed and productive as soon as possible.
\item Initiated and maintained a new public-facing knowledgebase for customers.
\end{itemize}
}
\tinyskip

\textbf{Senior systems administrator} -- Anchor & Apr 2007 -- Nov 2011 \\
\multicolumn{2}{p{15.6cm}}{
\myfonta
\begin{itemize}[topsep=1mm,itemsep=0.3mm,parsep=1.2mm]
\item Upgraded internal monitoring systems to implement escalation of alerts.
\item Introduced Puppet for automation of customer server builds, replacing cfengine.
\item Mentored new staff, working closely to get them settled in and up to speed.
%\item Developed automation tools to allow L1 support staff to safely and efficiently perform L2 tasks.
\item Performed forensic analysis and reporting following security breaches.
\item Developed processes for rapid virtualisation of physical servers, helping reduce operating costs.
\end{itemize}
}

\end{resumeblock}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
%\newpage



\begin{skillz}{Knowledge and experience}

\resumeitem{Operating Systems}{Extensive experience with Linux, primarily Redhat and Debian. Exposure to Windows 7/8/10, Server 2008 and 2012, some Exchange, some OS X}
\hugeplusskip

\resumeitem{Languages}{Heavy use of Python, shell, Perl, PHP, C, some Ruby and Java, Haskell and category theory}
\hugeplusskip

\resumeitem{Databases}{PostgreSQL, MySQL, SQLite, Redis, basic administration of MSSQL}
\hugeplusskip

\resumeitem{Networking}{Architecture and design, capacity planning, addressing and subnetting, routing and associated protocols, high availability, debugging, performance, IPsec and OpenVPN, IPv6, firewalls}
\hugeplusskip

\resumeitem{Security}{Policy, risk assessment, reporting, auditing, analysis, best practice, crypto}
\hugeplusskip

\resumeitem{Automation}{Puppet, automated OS installation with tools such as Kickstart and d-i, scripting with core unix utilities, etc.}
\hugeplusskip

\resumeitem{Webapps}{Common LAMP stack, nginx, WSGI, Rails via Thin/Unicorn/Passenger, Tomcat}
\hugeplusskip

\resumeitem{Scalability \& clustering}{HAproxy, Corosync and Pacemaker, DRBD}
\hugeplusskip

\resumeitem{People}{I am first and foremost a good listener. I communicate clearly and effectively in any medium, and can explain complex concepts to others regardless of their level of familiarity.}
\hugeplusskip

\end{skillz}



%\begin{resumeblock}{Keywords}
%
%\resumeitem{Operating Systems}{Strong knowledge of Linux (RHEL and Debian) and Windows}
%\shortskip
%
%\resumeitem{Languages}{Lots of Python, shell, Perl, PHP, C, some exposure to Ruby, Java, etc.}
%\shortskip
%
%\resumeitem{Databases}{PostgreSQL admin/replication/extension, MySQL admin, basic Oracle}
%\shortskip
%
%\resumeitem{Networking}{Architecture, addressing, routing, debugging, performance, VPNs, IPv6, firewalls}
%\shortskip
%
%\resumeitem{Security}{Policy, risk assessment, reporting, auditing, analysis, best practice, crypto}
%\shortskip
%
%\resumeitem{Automation}{Puppet, Ansible, automated OS installation, scripting core unix utilities, basic cfengine}
%\shortskip
%
%\resumeitem{Development}{Git and svn, software development methodologies, deployment best practices, RPM and DEB packaging, }
%\shortskip
%
%\resumeitem{Webapps}{LAMP stack, nginx, WSGI, Rails, Tomcat}
%\shortskip
%
%\resumeitem{People}{Listener, amicable, professional, courteous, level-headed}
%\largeskip
%
%\end{resumeblock}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
Bachelor of Science (Computer Science)\newline
University of New South Wales & 2002 -- 2006
\end{resumeblock}
\tinyskip


\end{document}
